---
title: 'Regression Fit '
output:
  html_document: default
  pdf_document: default
---
```{r readng all season stats}

```

#Just going to use the data to see what different methods of forecasting look like.
```{r Looking at All_Season_Stats}
install.packages("readr")
library("readr", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.4")
All_Season_Stats=read_csv("All_Season_Stats.csv")

tail(All_Season_Stats,25)
##The data as it stands could be reorganized, I am going to reorgainzie it by season with an emphasys on player age,so each player will have 5 observations at max.





```


#I'll Start by Making the data Set using the data from online

```{r Creating Name}

Name=rep(NA,6*length(All_Season_Stats$Player))#Making the data set full with NA's first, this will have 5 repeated names for each player and an extra for the predicted year, all data is total yearly for different stats

i=1 


while(floor(i/6)+1<=length(All_Season_Stats$Player)){###the floor(i/5)+1 always rounds to the first name for the first 5 entries and the second name for the next 5 entries

Name[i]=All_Season_Stats$Player[floor(i/6)+1]
Name[i+1]=All_Season_Stats$Player[floor(i/6)+1]
Name[i+2]=All_Season_Stats$Player[floor(i/6)+1]
Name[i+3]=All_Season_Stats$Player[floor(i/6)+1]
Name[i+4]=All_Season_Stats$Player[floor(i/6)+1]
Name[i+5]=All_Season_Stats$Player[floor(i/6)+1]
i=i+6
}
Name=as.factor(Name)
tail(Name,25)##Now names are factors that repeat 6 times in the data set for each name
```




```{r Creating Position}


Pos2=rep(NA,6*length(All_Season_Stats$Player))##This will repeat the position of the player listed in this data set, as I assume nobody changed for simplicity.



##Since my goal for this is the same as with name, to repeat the position 6 times, i will re use my old loop.

j=1 


while(floor(j/6)+1<=length(All_Season_Stats$Pos)){###the floor(j/5)+1 always rounds to the first position for the first 6 entries and the second position for the next 6 entries

Pos2[j]=All_Season_Stats$Pos[floor(j/6)+1]
Pos2[j+1]=All_Season_Stats$Pos[floor(j/6)+1]
Pos2[j+2]=All_Season_Stats$Pos[floor(j/6)+1]
Pos2[j+3]=All_Season_Stats$Pos[floor(j/6)+1]
Pos2[j+4]=All_Season_Stats$Pos[floor(j/6)+1]
Pos2[j+5]=All_Season_Stats$Pos[floor(j/6)+1]

j=j+6
}
Pos2=as.factor(Pos2)
tail(Pos2,25)##Now Pos2 is a vector of positions as factors

```

```{r Creating Age}



Age=rep(NA,6*length(All_Season_Stats$Player))##This will end up being a list of ages, starting at current age and going down one for the past years







k=1 


while(floor(k/6)+1<=length(All_Season_Stats$Pos)){###the floor(j/6)+1 always rounds to the first name for the first 6 entries and the second name for the next 6 entries

  

  
  
Age[k]=All_Season_Stats$Age[floor(k/6)+1]+1##Predicted age is one more then age in 2018
Age[k+1]=All_Season_Stats$Age[floor(k/6)+1]###Using the same old loop which repeats entries I edited it so that the following entries after every 5th is reduced by one, so now we should have a list of ages that the players were at during each season
Age[k+2]=All_Season_Stats$Age[floor(k/6)+1]-1
Age[k+3]=All_Season_Stats$Age[floor(k/6)+1]-2
Age[k+4]=All_Season_Stats$Age[floor(k/6)+1]-3
Age[k+5]=All_Season_Stats$Age[floor(k/6)+1]-4


k=k+6
}
tail(Age,25)

```

```{r Finiding year}

##Tm I am not going to use for anaylsys

#I won't be using games played, games started, or minutes played in the analysis

Year=rep(NA,6*length(All_Season_Stats$Player))##This will contain years 2019 through 2014

y=c(2019,2018,2017,2016,2015,2014)
Year=rep(y,length(All_Season_Stats$Player))

tail(Year,25)



```

```{r Finding FG}


FG=rep(NA,6*length(All_Season_Stats$Player))##This will contain a record of fieldgoals made on total in years each year 2014 to 2018

ii=2###Start at 2 because first entry for each player is year 2019 nobody has made any FG
while(ii<=(6*length(All_Season_Stats$Player))){
  
##First entry stays NA each time
FG[ii]=All_Season_Stats$FG_18[floor(ii/6)+1]
FG[ii+1]=All_Season_Stats$FG_17[floor(ii/6)+1]###Every 5th entry is the field goals for 18, and so on
FG[ii+2]=All_Season_Stats$FG_16[floor(ii/6)+1]
FG[ii+3]=All_Season_Stats$FG_15[floor(ii/6)+1]
FG[ii+4]=All_Season_Stats$FG_14[floor(ii/6)+1]

ii=ii+6
}
tail(FG,25)

```


```{r Finding Bhind_Arc}

#I won't be using field goals attempted

Bhind_Arc=rep(NA,6*length(All_Season_Stats$Player))##This will contain the 3 point field goals made per game through the years.

jj=2
while(jj<=(6*length(All_Season_Stats$Player))){
Bhind_Arc[jj]=All_Season_Stats$`3P_18`[floor(jj/6)+1]
Bhind_Arc[jj+1]=All_Season_Stats$`3P_17`[floor(jj/6)+1]###Every 5th entry is the 3 points made for 18, and so on
Bhind_Arc[jj+2]=All_Season_Stats$`3P_16`[floor(jj/6)+1]
Bhind_Arc[jj+3]=All_Season_Stats$`3P_15`[floor(jj/6)+1]
Bhind_Arc[jj+4]=All_Season_Stats$`3P_14`[floor(jj/6)+1]

jj=jj+6
}
tail(Bhind_Arc,25)


```



```{r finding In_Arc}
In_Arc=rep(NA,length(All_Season_Stats$Player))#This will contain 2 point field goals made total throughout the years



l=2
while(l<=(6*length(All_Season_Stats$Player))){
In_Arc[l]=All_Season_Stats$`2P_18`[floor(l/6)+1]
In_Arc[l+1]=All_Season_Stats$`2P_17`[floor(l/6)+1]###Every 5th entry is the 2 points made for 18, and so on
In_Arc[l+2]=All_Season_Stats$`2P_16`[floor(l/6)+1]
In_Arc[l+3]=All_Season_Stats$`2P_15`[floor(l/6)+1]
In_Arc[l+4]=All_Season_Stats$`2P_14`[floor(l/6)+1]

l=l+6
}
tail(In_Arc,25)

```


```{r finding FreeT}
FreeT=rep(NA,length(All_Season_Stats$Player))##This will contain free throws made total throughout the years

ll=2
while(ll<=(6*length(All_Season_Stats$Player))){
FreeT[ll]=All_Season_Stats$FT_18[floor(ll/6)+1]
FreeT[ll+1]=All_Season_Stats$FT_17[floor(ll/6)+1]###Every 5th entry is the free throw made for 18, and so on
FreeT[ll+2]=All_Season_Stats$FT_16[floor(ll/6)+1]
FreeT[ll+3]=All_Season_Stats$FT_15[floor(ll/6)+1]
FreeT[ll+4]=All_Season_Stats$FT_14[floor(ll/6)+1]

ll=ll+6
}
tail(FreeT,25)

```

```{r finding OfReb}

OfReb=rep(NA,length(All_Season_Stats$Player))##This will contain offensive rebound made total thruoghout the seasons



w=2
while(w<=(6*length(All_Season_Stats$Player))){
OfReb[w]=All_Season_Stats$ORB_18[floor(w/6)+1]
OfReb[w+1]=All_Season_Stats$ORB_17[floor(w/6)+1]###Every 5th entry is the offreb for 18, and so on
OfReb[w+2]=All_Season_Stats$ORB_16[floor(w/6)+1]
OfReb[w+3]=All_Season_Stats$ORB_15[floor(w/6)+1]
OfReb[w+4]=All_Season_Stats$ORB_14[floor(w/6)+1]

w=w+6

}
tail(OfReb,25)


```



```{r finding DefReb}
DefReb=rep(NA,length(All_Season_Stats$Player))##This will be like OfReb but for defensive rebounds



ww=2
while(ww<=(6*length(All_Season_Stats$Player))){
DefReb[ww]=All_Season_Stats$DRB_18[floor(ww/6)+1]
DefReb[ww+1]=All_Season_Stats$DRB_17[floor(ww/6)+1]###Every 5th entry is the defreb for 18, and so on
DefReb[ww+2]=All_Season_Stats$DRB_16[floor(ww/6)+1]
DefReb[ww+3]=All_Season_Stats$DRB_15[floor(ww/6)+1]
DefReb[ww+4]=All_Season_Stats$DRB_14[floor(ww/6)+1]

ww=ww+6

}
tail(DefReb,25)


##Not going to use total rebounds, as in the shiny app a user can just make OfReb and DefReb the same for this result


```


```{r finding assist}

Assist=rep(NA,length(All_Season_Stats$Player))##This will be the total  assists in each season



m=2
while(m<=(6*length(All_Season_Stats$Player))){
Assist[m]=All_Season_Stats$AST_18[floor(m/6)+1]
Assist[m+1]=All_Season_Stats$AST_17[floor(m/6)+1]###Every 5th entry is the assist for 18, and so on
Assist[m+2]=All_Season_Stats$AST_16[floor(m/6)+1]
Assist[m+3]=All_Season_Stats$AST_15[floor(m/6)+1]
Assist[m+4]=All_Season_Stats$AST_14[floor(m/6)+1]

m=m+6

}

tail(Assist,25)
```

```{r finding steals}

Steal=rep(NA,length(All_Season_Stats$Player))##This will be the total steals in each season

mm=2
while(mm<=(6*length(All_Season_Stats$Player))){
Steal[mm]=All_Season_Stats$STL_18[floor(mm/6)+1]
Steal[mm+1]=All_Season_Stats$STL_17[floor(mm/6)+1]###Every 5th entry is the steal for 18, and so on
Steal[mm+2]=All_Season_Stats$STL_16[floor(mm/6)+1]
Steal[mm+3]=All_Season_Stats$STL_15[floor(mm/6)+1]
Steal[mm+4]=All_Season_Stats$STL_14[floor(mm/6)+1]

mm=mm+6

}
tail(Steal,25)
```


```{r finding blocks}
Block=rep(NA,length(All_Season_Stats$Player))##This will be the total blocks in each season


q=2
while(q<=(6*length(All_Season_Stats$Player))){
Block[q]=All_Season_Stats$BLK_18[floor(q/6)+1]
Block[q+1]=All_Season_Stats$BLK_17[floor(q/6)+1]###Every 5th entry is the block for 18, and so on
Block[q+2]=All_Season_Stats$BLK_16[floor(q/6)+1]
Block[q+3]=All_Season_Stats$BLK_15[floor(q/6)+1]
Block[q+4]=All_Season_Stats$BLK_14[floor(q/6)+1]

q=q+6

}
tail(Block,25)
```



```{r finding Turnovers}

TOV=rep(NA,length(All_Season_Stats$Player))##This will be the total turnovers per game in each season


qq=2
while(qq<=(6*length(All_Season_Stats$Player))){
TOV[qq]=All_Season_Stats$TOV_18[floor(qq/6)+1]
TOV[qq+1]=All_Season_Stats$TOV_17[floor(qq/6)+1]###Every 5th entry is the turnover for 18, and so on
TOV[qq+2]=All_Season_Stats$TOV_16[floor(qq/6)+1]
TOV[qq+3]=All_Season_Stats$TOV_15[floor(qq/6)+1]
TOV[qq+4]=All_Season_Stats$TOV_14[floor(qq/6)+1]

qq=qq+6

}


tail(TOV,25)
```


```{r finding fouls }
Fouls=rep(NA,length(All_Season_Stats$Player))##This will be the average fouls per game in each season


s=2
while(s<=(6*length(All_Season_Stats$Player))){
Fouls[s]=All_Season_Stats$PF_18[floor(s/6)+1]
Fouls[s+1]=All_Season_Stats$PF_17[floor(s/6)+1]###Every 5th entry is the turnover for 18, and so on
Fouls[s+2]=All_Season_Stats$PF_16[floor(s/6)+1]
Fouls[s+3]=All_Season_Stats$PF_15[floor(s/6)+1]
Fouls[s+4]=All_Season_Stats$PF_14[floor(s/6)+1]

s=s+6

}
tail(Fouls,25)




##I won't be using points as we can just do 3 * 3 pointers made 2 * field goals made and 1 * free throws made

```

  




```{r the data set}
DatSet=data.frame(Name,Pos2,Age,Year,FG,Bhind_Arc,In_Arc,FreeT,OfReb,DefReb,Assist,Steal,Block,TOV,Fouls)
tail(DatSet,25)

```



#Now I will test a method of modeling with field goals



```{r model for FG}
fit1=glm(FG~I(Age^2)+Age+Name)
head(fit1$coefficients,5)


```





```{r predict}
pred_FG01=predict(fit1,DatSet)
DatSet01=data.frame(DatSet,pred_FG01)
tail(DatSet01,5)

```



```{r ggplot}

install.packages("ggplot2")
library("ggplot2", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.4")


```

```{r graphs}
GraphFG_Name=function(Name){
 ii=(which(All_Season_Stats$Player==Name))
ggplot(DatSet01[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=FG,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_FG01,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_FG01,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Field Goal's of ",Name),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Field Goals",
 color = "Actual or Predicted")
}
GraphFG_Num=function(ii){

ggplot(DatSet01[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=FG,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_FG01,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_FG01,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Field Goal's of ",All_Season_Stats$Player[ii]),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Field Goals",
 color = "Actual or Predicted")
}
```











```{r install dplyr}
install.packages("dplyr")
library("dplyr", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.4")
```

















```{r}

GraphFG_Num(442)

```








#Since that seemed to work so well I will now model all of the attributes with functions like I did field goals









```{r More Fits}
fit_Bhind_Arc=glm(Bhind_Arc~I(Age^2)+Age+Name)##A fit for 3 points made total in a season
head(fit_Bhind_Arc$coefficients,5)

fit_In_Arc=glm(In_Arc~I(Age^2)+Age+Name)##A fit for 2 points made total in a season
head(fit_In_Arc$coefficients,5)

fit_FreeT=glm(FreeT~I(Age^2)+Age+Name)##A fit for free throws made total in a season
head(fit_FreeT$coefficients,5)


fit_OfReb=glm(OfReb~I(Age^2)+Age+Name)##A fit for offensive rebounds made total in a season
head(fit_OfReb$coefficients,5)


fit_DefReb=glm(DefReb~I(Age^2)+Age+Name)##A fit for defensive rebounds made total in a season
head(fit_DefReb$coefficients,5)


fit_Assist=glm(Assist~I(Age^2)+Age+Name)##A fit for assists made total in a season
head(fit_Assist$coefficients,5)

fit_Steal=glm(Steal~I(Age^2)+Age+Name)##A fit for Steals made total in a season
head(fit_Steal$coefficients,5)

fit_Block=glm(Block~I(Age^2)+Age+Name)##A fit for Blocks made total in a season
head(fit_Block$coefficients,5)

fit_TOV=glm(TOV~I(Age^2)+Age+Name)##A fit for turnovers made total in a season
head(fit_TOV$coefficients,5)

fit_Fouls=glm(Fouls~I(Age^2)+Age+Name)##A fit for Fouls made total in a season
head(fit_Fouls$coefficients,5)
```





```{r More Predictins}
pred_Bhind_Arc=predict(fit_Bhind_Arc,DatSet)#Predictions for players 3 point totals in a season at 6 different ages, one being the future

pred_In_Arc=predict(fit_In_Arc,DatSet)#Predictions for players 2 point totals in a season at 6 different ages, one being the future

pred_FreeT=predict(fit_FreeT,DatSet)#Predictions for players free throw totals in a season at 6 different ages, one being the future

pred_OfReb=predict(fit_OfReb,DatSet)#Predictions for players offensive rebound totals in a season at 6 different ages, one being the future

pred_DefReb=predict(fit_DefReb,DatSet)#Predictions for players defencsive rebounds totals in a season at 6 different ages, one being the future

pred_Assist=predict(fit_Assist,DatSet)#Predictions for players assists totals in a season at 6 different ages, one being the future

pred_Steal=predict(fit_Steal,DatSet)#Predictions for players assists totals in a season at 6 different ages, one being the future

pred_Block=predict(fit_Block,DatSet)#Predictions for players blocks totals in a season at 6 different ages, one being the future

pred_TOV=predict(fit_TOV,DatSet)#Predictions for players turnovers totals in a season at 6 different ages, one being the future

pred_Fouls=predict(fit_Fouls,DatSet)#Predictions for players Fouls totals in a season at 6 different ages, one being the future


DatSetPrime=data.frame(DatSet,pred_Bhind_Arc,pred_In_Arc,pred_FreeT,pred_OfReb,pred_DefReb,pred_Assist,pred_Steal,pred_Block,pred_TOV,pred_Fouls)
tail(DatSetPrime,5)##The data set with all the predictions

```




```{r Functions for 3 pointers} 

Graph_Bhind_Arc_Name=function(Name){###Graphing behind the arc using functions with either name strings or numbers as inputs
 ii=(which(All_Season_Stats$Player==Name))
ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=Bhind_Arc,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_Bhind_Arc,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_Bhind_Arc,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted 3 pointers made of ",Name),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="3 Pointers Made",
 color = "Actual or Predicted")
}




Graph_Bhind_Arc_Num=function(ii){

  
  ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=Bhind_Arc,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_Bhind_Arc,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_Bhind_Arc,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted 3 pointers made of ",All_Season_Stats$Player[ii]),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="3 Pointers Made",
 color = "Actual or Predicted")
  
  
  
  
  
  
  
  
  
  
  
}

```





```{r Testing 3 point graphs}
Graph_Bhind_Arc_Num(466)
```

```{r Functions for 2 pointers} 

Graph_In_Arc_Name=function(Name){###Graphing in the arc using functions with either name strings or numbers as inputs
 ii=(which(All_Season_Stats$Player==Name))
ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=In_Arc,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_In_Arc,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_In_Arc,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted 2 pointers made of ",Name),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="2 Pointers Made",
 color = "Actual or Predicted")
}




Graph_In_Arc_Num=function(ii){

  

  
  
  ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=In_Arc,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_In_Arc,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_In_Arc,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted 2 pointers made of ",All_Season_Stats$Player[ii]),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="2 Pointers Made",
 color = "Actual or Predicted")
}
  

```



```{r Testing 2 point graphs }

Graph_In_Arc_Name("Anthony Davis")


```


```{r Functions for free throws} 

Graph_FreeT_Name=function(Name){###Graphing free throws using functions with either name strings or numbers as inputs
 ii=(which(All_Season_Stats$Player==Name))
ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=FreeT,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_FreeT,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_FreeT,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Free Throws made of ",Name),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Free Throws Made",
 color = "Actual or Predicted")
}




Graph_FreeT_Num=function(ii){

  

  ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=FreeT,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_FreeT,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_FreeT,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Free Throws made of ",All_Season_Stats$Player[ii]),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Free Throws Made",
 color = "Actual or Predicted")
}
 

```



```{r Testing free throw graphs}
Graph_FreeT_Name("James Harden")
```



```{r Functions for Of Rebounds} 

Graph_OfReb_Name=function(Name){###Graphing Offensive Rebounds using functions with either name strings or numbers as inputs
 ii=(which(All_Season_Stats$Player==Name))
ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=OfReb,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_OfReb,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_OfReb,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Offensive Rebounds made of ",Name),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Offensive Rebounds",
 color = "Actual or Predicted")
}




Graph_OfReb_Num=function(ii){

  ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=OfReb,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_OfReb,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_OfReb,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Offensive Rebounds made of ",All_Season_Stats$Player[ii]),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Offensive Rebounds",
 color = "Actual or Predicted")
}


 

```


```{r Testing graphing ofreb}
Graph_OfReb_Name("Andre Drummond")
Graph_OfReb_Num(466)
```




```{r Functions for Deff Rebounds} 

Graph_DefReb_Name=function(Name){###Graphing defensive Rebounds using functions with either name strings or numbers as inputs
 ii=(which(All_Season_Stats$Player==Name))
ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=DefReb,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_DefReb,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_DefReb,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Defensive Rebounds made of ",Name),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Defensive Rebounds",
 color = "Actual or Predicted")
}




Graph_DefReb_Num=function(ii){

  ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=DefReb,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_DefReb,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_DefReb,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Defensive Rebounds made of ",All_Season_Stats$Player[ii]),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Defensive Rebounds",
 color = "Actual or Predicted")
}
  

 

```





```{r Testing dfReb}

Graph_DefReb_Name("LeBron James")
```



```{r Functions for Assists} 

Graph_Assist_Name=function(Name){###Graphing defensive Rebounds using functions with either name strings or numbers as inputs
 ii=(which(All_Season_Stats$Player==Name))
ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=Assist,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_Assist,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_Assist,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted assists made of ",Name),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Assists",
 color = "Actual or Predicted")
}




Graph_Assist_Num=function(ii){
  
  
  ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=Assist,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_Assist,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_Assist,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted assists made of ",All_Season_Stats$Player[ii]),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Assists",
 color = "Actual or Predicted")
}



```



```{r testing graph assist}
Graph_Assist_Name("James Harden")
```


```{r Functions for Steal} 

Graph_Steal_Name=function(Name){###Graphing defensive Rebounds using functions with either name strings or numbers as inputs
 ii=(which(All_Season_Stats$Player==Name))
ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=Steal,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_Steal,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_Steal,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted steal made of ",Name),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Steals",
 color = "Actual or Predicted")
}




Graph_Steal_Num=function(ii){
  
  
  ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=Steal,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_Steal,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_Steal,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted steal made of ",All_Season_Stats$Player[ii]),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Steals",
 color = "Actual or Predicted")
}
  



```





```{r tesing graph steal}
Graph_Steal_Name("Rajon Rondo")

```




```{r Functions for Block} 

Graph_Block_Name=function(Name){###Graphing defensive Rebounds using functions with either name strings or numbers as inputs
 ii=(which(All_Season_Stats$Player==Name))
ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=Steal,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_Block,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_Block,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Block made of ",Name),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Block",
 color = "Actual or Predicted")
}




Graph_Block_Num=function(ii){
  
  
 ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=Steal,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_Block,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_Block,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Block made of ",All_Season_Stats$Player[ii]),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Block",
 color = "Actual or Predicted")
}
  


```





```{r testing graph block}
Graph_Block_Name("LeBron James")
Graph_Block_Num(466)
```

```{r Functions for TOV} 

Graph_TOV_Name=function(Name){###Graphing defensive Rebounds using functions with either name strings or numbers as inputs
 ii=(which(All_Season_Stats$Player==Name))
ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=TOV,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_TOV,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_TOV,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted TOV made of ",Name),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="TOV",
 color = "Actual or Predicted")
}




Graph_TOV_Num=function(ii){
  
  
  
  ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=TOV,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_TOV,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_TOV,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted TOV made of ",All_Season_Stats$Player[ii]),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="TOV",
 color = "Actual or Predicted")
}

  


```


```{r testing graph TOV}
Graph_TOV_Name("James Harden")
Graph_TOV_Num(466)
```


```{r Functions for Fouls} 

Graph_Fouls_Name=function(Name){###Graphing defensive Rebounds using functions with either name strings or numbers as inputs
 ii=(which(All_Season_Stats$Player==Name))
ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=Fouls,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_Fouls,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_Fouls,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Fouls made of ",Name),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Fouls",
 color = "Actual or Predicted")
}




Graph_Fouls_Num=function(ii){
  
  
  ggplot(DatSetPrime[(6*ii-5):(6*ii),],mapping=aes(x=Age, y=Fouls,color="Actual"))+geom_line(mapping=aes(x=Age,y=pred_Fouls,color="Predicted Curve"))+geom_point(mapping=aes(x=Age,y=pred_Fouls,color="Predicted"))+geom_point()+
labs(title = paste0("Predicted Fouls made of ",All_Season_Stats$Player[ii]),
 subtitle = "Based on data from 2014 to 2018",
 x = "Age",
 y ="Fouls",
 color = "Actual or Predicted")
}


  


```



```{r testing graph fouls}
Graph_Fouls_Name("Russell Westbrook")
Graph_Fouls_Num(466)
```
#Now That I have predictions functions for all of them I can make a function of functions


```{r MegaFun}
MegFun=function(Player_Name="",iii=0,Bhind_Arc=F,In_Arc=F,FreeT=F,OfReb=F,DefReb=F,Assist=F,Steal=F,Block=F,TOV=F,Fouls=F){
  if(Name==""&ii==0){
    return("Enter A Name or Number")##The function is writen so that if you enter a Name then the number doesnt matter
  }
  else if(Player_Name==""){
    Player_Name=All_Season_Stats$Player[iii]##but if u dont enter a Name then the number finds the name if it exists
  }
  if(Bhind_Arc==T){
    return(Graph_Bhind_Arc_Name(Player_Name))##Do to how return works it only outputs on graph at once
  }
  else if(In_Arc==T){
    return(Graph_In_Arc_Name(Player_Name))##and that graph is the leftmost true value
  }
  else if(FreeT==T){
    return(Graph_FreeT_Name(Player_Name))##in the future we can update it so it can return more then one graph, as well as different graphs
  }
  if(OfReb==T){
    return(Graph_OfReb_Name(Player_Name))
  }
    if(DefReb==T){
    return(Graph_DefReb_Name(Player_Name))
  }
  if(Assist==T){
    return(Graph_Assist_Name(Player_Name))
  }
  if(Steal==T){
    return(Graph_Steal_Name(Player_Name))
  }
  if(Block==T){
    return(Graph_Block_Name(Player_Name))
  }
  if(TOV==T){
    return(Graph_TOV_Name(Player_Name))
  }
   if(Fouls==T){
    return(Graph_Fouls_Name(Player_Name))
  }

  
  
  
}
```


```{r testing megafun}
MegFun(Player_Name="LeBron James",DefReb=T)
```


